An Experimental Evaluation of Hybrid Querying on Vectors (EA\&B)

### 2025-07-23 VLDB2026/main.tex
1

	\textit{\textbf{ \textcolor{orange}{Search peak memory.}}}
%	 \textcolor{orange}{As shown in Figure~\ref{fig:search_memory_mb_comparison}, we can find that the peak memory usage of each algorithm during search does not differ significantly. Among them, CAPS and NHQ have relatively higher peak memory usage, while the peak memory usage of database is comparatively lower.}
	\textcolor{orange}{For most algorithms, the query phase requires loading both the index and the dataset into memory, so its peak memory usage is usually comparable to that of the construction phase. However, as shown in the Figure~\ref{fig:search_memory_mb_comparison}, CAPS exhibits significantly higher peak memory during querying due to the need to dynamically maintain large candidate sets. In contrast, Milvus has lower query-time memory usage because it does not fully load the index and incurs additional metadata overhead during construction.
	}
	\subsubsection{Performance Evaluation}

@@

	(1) \textit{Algorithms optimized for low AS.}  
	This group includes ACORN-1, CAPS, StitchedVamana, UNG, Puck, Faiss, and Faiss+HQI\_Batch as illustrated in Figure~\ref{fig:exp_5_2_1}.

>>>>

\textit{\textbf{ \textcolor{orange}{Search peak memory.}}}
%  \textcolor{orange}{As shown in Figure~\ref{fig:search_memory_mb_comparison}, we can find that the peak memory usage of each algorithm during search does not differ significantly. Among them, CAPS and NHQ have relatively higher peak memory usage, while the peak memory usage of database is comparatively lower.}
\textcolor{orange}{For most algorithms, the query phase requires loading both the index and the dataset into memory, so its peak memory usage is usually comparable to that of the construction phase. However, as shown in the Figure~\ref{fig:search_memory_mb_comparison}, CAPS exhibits significantly higher peak memory during querying due to the need to dynamically maintain large candidate sets. In contrast, Milvus has lower query-time memory usage because it does not fully load the index and incurs additional metadata overhead during construction.
}

	\subsubsection{Performance Evaluation}

@@

	(1) \textit{Algorithms optimized for low AS.}  
	This group includes ACORN-1, Faiss+HQI\_Batch, StitchedVamana, UNG, Faiss, Puck, and CAPS, as illustrated in Figure~\ref{fig:exp_5_2_1}.
